---
title: "Data cleaning project"
author: "Fan Yang"
date: "3/18/2019"
output: html_document
---
```{r}
library("dplyr")
```

#read the heart.csv file 
```{r }
tuna <- read.csv("2020.csv", TRUE)
head(tuna)
str(tuna)
```
#Check the NA values in the dataset
#There is no Missing Value in the Dataset 
```{r}
is.na(tuna)
```
## Rename certain columns ot the dataset.
# Renmae cp to ChestPain and fbs to fbs120
```{r}
tuna <- rename(tuna, fbs120=fbs, ChestPain=cp)
head(tuna)
```
# Create a new variable by substracting the meanage from age
```{r}
tuna<- mutate(tuna, mean(age)-age)
head(tuna)
```
# Filter by extracting subsets of rows from a dataset
```{r}
tunaa <- filter(tuna,sex <1 & oldpeak>0)
head(tunaa)
```
```
#Use select to show dataset that only contains Sex and oldpeak variables 
```{r}
 head(select(tunaa,sex,oldpeak))
```
# Create a new variable Year by adding age to 1900
# Group the dataset by the new variable Year
```{r}
tunaa <- mutate(tuna, year = age+1900)
tunaaa <- group_by(tunaa,year)
summarize(tunaaa, chol=mean(chol))
```

